Step 10: Pool Results Across PS Methods Using Rubin's Rules

### 2025-09-08 reanalysis-10-pooling_results.qmd
refactor forest plot

## Forest Plot

```{r forest-plot}
#| fig.height: 10
#| fig.width: 8

if (length(pooled_results) > 0) {
  # Format data for forest plot
  forest_data <- format_for_forest_plot(pooled_results)

  # Add colors for specific methods
  forest_data$color <- "black"
  if ("twang_gbm" %in% forest_data$method) {
    forest_data$color[forest_data$method == "twang_gbm"] <- "blue"
  }

  # Create the plot
  forest_plot <- ggplot(forest_data, aes(x = reorder(method_label, or), y = or)) +
    geom_pointrange(aes(ymin = lower, ymax = upper, color = color), size = 0.8) +
    geom_point(aes(color = color), size = 3) +
    geom_text(aes(label = sprintf("%.2f", or), color = color), 
              vjust = -1.2, hjust = 0.5, size = 4) +
    coord_flip() +
    scale_color_identity() +
    scale_y_continuous(breaks = seq(0.5, max(forest_data$upper, 1.5), by = 0.1),
                       trans = "log",
                       labels = function(x) sprintf("%.1f", x)) +
    scale_x_discrete(expand = c(0.075, 0.075)) +
    theme_minimal(base_size = 14) +
    labs(
      x = element_blank(),
      y = "Odds Ratio",
      title = "Propensity Score Method Comparison",
      subtitle = "Pooled estimates across multiple imputations using mice package (Rubin's rules)",
      caption = "All methods use ATT (Average Treatment Effect in the Treated) estimand"
    ) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold", margin = margin(b = 10)),
      plot.subtitle = element_text(hjust = 0.5, margin = margin(b = 15)),
      legend.position = "none",
      axis.line = element_line(color = "gray80"),
      axis.text = element_text(color = "gray30"),
      axis.ticks = element_line(color = "gray80"),
      axis.title.x = element_text(margin = margin(t = 10)),
      plot.caption = element_text(margin = margin(t = 15), hjust = 0),
      plot.margin = margin(20, 20, 30, 20)
    ) +
    geom_hline(yintercept = 1, linetype = "dashed", color = "gray70")

  print(forest_plot)

  # Save the plot
  ggsave(
    filename = file.path(reanalysis_data_dir, "forest_plot_pooled_results.png"),
    plot = forest_plot,
    width = 10,
    height = 8,
    dpi = 300
  )

  log_message("Forest plot saved")
} else {
  cat("No pooled results available for forest plot\n")
}
```

>>>>

## Results Summary

```{r results-summary}
if (length(pooled_results) > 0) {
  cat("\n", paste(rep("=", 60), collapse = ""), "\n")
  cat("POOLING RESULTS SUMMARY\n")
  cat(paste(rep("=", 60), collapse = ""), "\n\n")

  # Count successful methods
  n_success <- sum(sapply(pooled_results, function(x) x$success))
  cat("Successfully pooled:", n_success, "of", length(pooled_results), "methods\n\n")

  # Show OR range
  or_values <- sapply(pooled_results, function(x) if(x$success) x$or else NA)
  or_values <- or_values[!is.na(or_values)]

  if (length(or_values) > 0) {
    cat(sprintf("OR range: %.3f to %.3f\n", min(or_values), max(or_values)))
    cat(sprintf("Median OR: %.3f\n", median(or_values)))
  }

  cat("\nForest plot visualization can be generated using:\n")
  cat("  reanalysis-11-forest_plot.qmd\n")

  log_message(paste0("Pooling complete. ", n_success, " methods successfully pooled."))
} else {
  cat("No pooled results available\n")
}
```
